To Compete or Cooperate? This is the Question in Communities of Autonomous Services

### 2014-02-01 papers/coop-journal-R1/coop_response_letter.tex

\vspace{0.5cm} \textbf{\underline{2. Reviewer}}:  Introduction: The first phrase ``Services are software systems...'' should include which kind of services are being analysed: intelligent, autonomous,... The definition used does not correspond to ``Services'' as a whole.

\vspace{0.2cm}\textbf{\underline{Answer 2}: We agree, the definition was too broad we rephrased
the sentence as follows: Online Services are software systems providing a standard way of
interoperability among different applications. These services are developed
 in an autonomous and intelligent manner to continuously and autonomously interact with each other to
fulfill users' requests.}

\vspace{0.5cm} \textbf{\underline{3. Reviewer}}: Related work: The authors state in page 21: ``The interesting idea is to consider the benefits under four categories: innovation and learning,...''. If this is an interesting idea, it should be further explained. I agree with the authors, these benefits are very interesting, please provide further details.

\vspace{0.2cm}\textbf{\underline{Answer 3}: In the revised manuscript, page 21 we added more description about their framework. Here is the quick summary of their definitions as we added to paper: \emph{Innovation and learning perspective} focuses on the knowledge, skills, and systems needed to improve the business continually. Necessary factors to build strategic capabilities and efficiency in addressed in internal business process. Values that customers seek are considered in \emph{customer perspective} and financial performance to maximize the shareholder value are analyzed in \emph{financial perspective}. Their goal is to design the framework for cooperating web services, inline with business strategy of firms in IT industry.}

@@

\vspace{0.5cm} \textbf{\underline{4. Reviewer}}:  Conclusion: The paper identifies clearly the implications for practice and further research. I consider the service consumer role very interesting for future research.

\vspace{0.2cm}\textbf{\underline{Answer 4}: Thanks for your comment. As mentioned in the manuscript, this is something we are considering as our furutre work. A case study in which we can collect user feedback, and adding it as a system parameter in our algorithm can improve our decision making process from users perspective which will lead to more efficiency, payoff and income for our web services}

### 2014-02-01 papers/coop-journal-R1/BNJ Exp Sys App.tex
changes

At the best of our knowledge, there is no work in the literature
of service and agent computing addressing the issue of coopetition
strategies and when to cooperate or to compete. However, some
relevant proposals to the model presented in this paper are the
ones that address service selection and task allocation
mechanisms. In many frameworks proposed in the literature, service
selection and task allocation are regulated based on the
reputation parameter \cite{Bentahar,Rosario,Ruth,Yahyaoui}. In
\cite{Huang}, the authors propose a framework to match potential
benefits of services while cooperating with one another. The
interesting idea is to consider the benefits under four
categories: innovation and learning, internal business process,
customer, and financial benefits. In \cite{Alchieri}, the authors
present a dependable framework for cooperative service agents that
is based on the tuple space coordination model. The
intrusion-tolerant perspective is emphasized in this paper where
several security mechanisms are developed to enable a reliable
coordination system. %In \cite{Maximilien2}, authors propose
%ontology for quality of service. Users compute the web services'
%reputation using ratings.
The proposed frameworks mostly aim to facilitate the coordination
mechanism between services. However, the opposite strategy of
competing is not analyzed where services might be more successful
when competing within the same group. In fact, services are not
always willing to cooperate even if they have some common goals,
particularly when they operate within groups such as communities.
In such a context, service agents can follow different interacting
strategies and have to decide when to compete and when to
cooperate so that their ultimate goal, maximizing their incomes,
can be better achieved. In our framework, we analyze those
different strategies to help services in their decision making
process when these
agents function within communities. %We summarize most of
%these proposals and concentrate on strategic decision making
%system that ranks web services in the community and analyze their
%effective interacting strategies to accomplish continuous
%requested tasks.
We enable service agents to reasonably evaluate and decide over
their coopetition strategies, which means deciding when to compete
and when to cooperate.

>>>>

At the best of our knowledge, there is no work in the literature
of service and agent computing addressing the issue of coopetition
strategies and when to cooperate or to compete. However, some
relevant proposals to the model presented in this paper are the
ones that address service selection and task allocation
mechanisms. In many frameworks proposed in the literature, service
selection and task allocation are regulated based on the
reputation parameter \cite{Bentahar,Rosario,Ruth,Yahyaoui}. 
\textbf{In \cite{Huang}, the authors propose a framework to match potential
benefits of services while cooperating with one another. The
interesting idea is to consider the benefits under four
categories: innovation and learning, internal business process,
customer, and financial benefits. 
\emph{Innovation and learning perspective} focuses on the knowledge, skills, and systems needed to improve the business continually. Necessary factors to build strategic capabilities and efficiency in addressed in internal business process. Values that customers seek are considered in \emph{customer perspective} and financial performance to maximize the shareholder value are analyzed in \emph{financial perspective}. Their goal is to design the framework for cooperating web services, inline with business strategy of firms in IT industry.}
In \cite{Alchieri}, the authors
present a dependable framework for cooperative service agents that
is based on the tuple space coordination model. The
intrusion-tolerant perspective is emphasized in this paper where
several security mechanisms are developed to enable a reliable
coordination system. %In \cite{Maximilien2}, authors propose
%ontology for quality of service. Users compute the web services'
%reputation using ratings.
The proposed frameworks mostly aim to facilitate the coordination
mechanism between services. However, the opposite strategy of
competing is not analyzed where services might be more successful
when competing within the same group. In fact, services are not
always willing to cooperate even if they have some common goals,
particularly when they operate within groups such as communities.
In such a context, service agents can follow different interacting
strategies and have to decide when to compete and when to
cooperate so that their ultimate goal, maximizing their incomes,
can be better achieved. In our framework, we analyze those
different strategies to help services in their decision making
process when these
agents function within communities. %We summarize most of
%these proposals and concentrate on strategic decision making
%system that ranks web services in the community and analyze their
%effective interacting strategies to accomplish continuous
%requested tasks.
We enable service agents to reasonably evaluate and decide over
their coopetition strategies, which means deciding when to compete
and when to cooperate.
